PK object batch mode trial

### 2023-09-11 data-raw/batchMode_trial_gpm.Rmd
Added a time conversion table and made slight optimizations to the parameter assignment for the functions doing tkstat, concentration, or auc calculations.

my_pk <- do_prefit(my_pk) # needs reframe somewhere
# Timing for normal fit sapply
{
  start_t <- Sys.time()
  my_pk <- do_fit(my_pk, n_cores = 6)
  round(Sys.time() - start_t, 3) # 5.741min (5 data_groups)
}
# my_pk <- do_fit(my_pk)
{
  start_t <- Sys.time()
  my_pk_time_scaling <- do_fit(my_pk_time_scaling, n_cores = 10)
  round(Sys.time() - start_t, 3) # w/ Time scaling 36mins!
}

@@

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "time_units",
                  # descendents = FALSE,
                  # ancestors = FALSE,
                  border = TRUE, cex = 1, lwd = 1.5)

@@

  myRMSE_all <- rmse(obj,
                     rmse_group = vars(Route, Media, Dose),
                     use_scale_conc = FALSE) %>% 
    inner_join(winning_model) %>%
    dplyr::group_by(!!!obj$data_group, model, method) %>%
    dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4),
                     median_MSE = median(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4))

  my_df <- left_join(fold_errors_all, r2_df) %>%
    inner_join(myAIC) %>%
    inner_join(myRMSE_all) %>%
    mutate(Options = pk_name, .before = Chemical) %>%
    dplyr::select(!c("model_1comp", "model_2comp", "model_flat"))

@@

>>>>

my_pk <- do_prefit(my_pk) # needs reframe somewhere
# Timing for normal fit sapply
{
  start_t <- Sys.time()
  my_pk <- do_fit(my_pk, n_cores = 3)
  round(Sys.time() - start_t, 3) # 5.741min (5 data_groups)
} # 1.639min with only one dataset
# my_pk <- do_fit(my_pk)
{
  start_t <- Sys.time()
  my_pk_time_scaling <- do_fit(my_pk_time_scaling, n_cores = 10)
  round(Sys.time() - start_t, 3) # w/ Time scaling 36mins!
}

@@

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "convert_time",
                  # descendents = FALSE,
                  # ancestors = FALSE,
                  border = TRUE, cex = 1, lwd = 1.5)

@@

  myRMSE_all <- rmse(obj,
                     rmse_group = vars(Route, Media, Dose),
                     use_scale_conc = FALSE) %>% 
    inner_join(winning_model) %>%
    dplyr::group_by(!!!obj$data_group, model, method) %>%
    dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4),
                     median_MSE = median(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4))
  browser()
  my_df <- left_join(fold_errors_all, r2_df) %>%
    inner_join(myAIC) %>%
    inner_join(myRMSE_all) %>%
    mutate(Options = pk_name, .before = Chemical) %>%
    dplyr::select(!c("model_1comp", "model_2comp", "model_flat"))

@@

time_table <- convert_time_table()

time_table$TimeA %>% clipr::write_clip()
time_table$TimeB %>% clipr::write_clip()
time_table$conversion %>% MASS::fractions(max.denominator = 1000000000000000)

### Plotting for all (2GB file)
pdf(file = paste0(Sys.getenv("FIG_DIR"),
              "DoseNormalized_Joint_AllFits.pdf"))
for (i in 1:nrow(pl)) {
  print(pl$final_plot[[i]])
}
dev.off()
